% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Work Experience and Education}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
 \experience
    {Now}       {Machine Learning Engineer}{Hellofresh}{Berlin (Germany)}
    {October 2018}  {Made production-ready, deployed, enhanced and maintained models predicting the churn probability of active customers.}
                    {Python, AWS, Numpy, Pandas, Scikit-learn, Docker, Airflow, Hadoop, Impala}
  \emptySeparator
  \experience
    {September 2018}       {Lead Software Developer}{Infinitec in Finleap}{Berlin (Germany)}
    {March 2018}  {Managed and developed a live-chat software, a chatbot and the auditing layer of a financial platform.}
                    {Microservices, Docker, AWS, Gitlab, Python, Spacy, Rasa-NLU, Java 8, Spring Boot, Dropwizard, Javascript, Node.js, React, MongoDB, Redis, Graylog}
  \emptySeparator
  \experience
    {November 2017}   {Data Scientist}{Data Science Retreat}{Berlin (Germany)}
    {August 2017}  {Studied and practiced Machine Learning and Data Science with Python. Created a web portal aggregating IT articles from different sources relating the same story: \homepage{www.techcontroversy.com}
			}
                    {Python, Gensim, Pandas, Spacy, Scikit-learn, MySql, Flask, Jinja2, AWS}
  \emptySeparator
  \experience
    {July 2017} {IT Project Manager}{Comarch SA}{Cracow (Poland)}
    {July 2013} {Managed the integration a Personal Financial Management software into the portals of several banks.}
                    {Java, J2EE, Spring, Hibernate, Websphere, Freemarker, Javascript, Angular.js, Python, REST/JSON}
  \emptySeparator
  \experience
    {June 2013}    {Senior Developer and Consultant}{Pentasys AG}{München (Germany)}
    {January 2010} {Developed several parts of the web and mobile portal of a mobile network operator, and an application for the management of the configuration of trucks.}
                    {Java, Spring, Wicket, EJB, Struts, Jboss, Tomcat, Maven, Javascript, JQuery, Node.js, JAX-RS, JAXP}
  \emptySeparator
  \experience
  {December 2009}   {Senior Developer and Consultant}{Saxonia Systems AG}{München (Germany)}
  {October 2005}    {
  					    Developed and enhanced several modules of an ERP application for drugstores.
  					}   
                    {Java, J2EE, EJB, Swing, JBoss, Spring, Sybase, Ant}
  \emptySeparator
  \consultantexperience
  {September 2005}   {Junior Developer and Consultant}{Arvato Systems Technologies}{München (Germany)}
  {April 2000}       {
                     	  Developed several web applications for the intranet of a consulting company.
                     }
                     {Java, J2EE, Oracle DB, JDBC, Struts, Oracle Application Server, Javascript}
  \emptySeparator
  \consultantexperience
  {March 2000}  	{Junior Developer and Consultant}{Icon srl}{Verona (Italy)}
  {June 1999}   	{ 
  				 		Enhanced an applet for the inventorization of devices of a mobile network operator.
  				 	}
                	{Java, J2EE, Oracle, JDBC, Swing} 
   \emptySeparator
  \consultantexperience
  {March 1998}  	{Computer Engineering Degree}{Universita degli studi}{Modena/Pavia(Italy}
  {November 1991}   	{Main focus: Computer Engineering, Computer Science, Electrical Engineering, Control systems, Mathematics, Economics, C}
                	{C/C++, Pascal, Fortran, Prolog, Assembler 8086/Z80, Matlab}   
\end{experiences}

